### 2011-04-06 msm2ca.tex
update.

	\subsection{Working with finite fields}
	In $\mathbb{F}_p = \mathbb{Z}_p$ you can simply do the operations in modulo $p$.
	\[
		x \oplus y := x + y mod p,
	\]
	\[
		x \otimes y := xy mod p
	\]
	Subtration and division are subsituted with addition and multiplication:
	\[
		x - y := x + (-y),
	\]
	\[
		\frac{x}{y} := xy^{-1}
	\]

	\subsubsection{Operations for $\mathbb{F}_4$}
	For any finite field you can use precomupted addition/multiplication tables.
	\[
		\begin{array}{c | c c c c}
			+ & 0 & 1 & a & b \\
			\hline
			0 & 0 & 1 & a & b \\
			1 & 1 & 0 & b & a \\ 
			a & a & b & 0 & 1 \\
			b & b & a & 1 & 0
		\end{array}
		\quad
		\begin{array}{c|cccc}
			\cdot & 0 & 1 & a & b \\
			\hline
			0 & 0 & 0 & 0 & 0 \\
			1 & 0 & 1 & a & b \\
			a & 0 & a & b & 1 \\
			b & 0 & b & 1 & a
		\end{array}
	\]
	In $\mathbb{F}_4$, note that $-0 = 0$, $-1 = 1$, $-a = a$, and $-b = b$.

\section{Vector Spaces}
	\begin{defn}
		A vector space over the field of scalars $\mathbb{F}_4$ is a set $V$, whose elements are vectors, together with two binary operations addition and multiplication. The following axioms hold for addition
		\begin{itemize}
			\item Associative: $\forall u,v,w \in V, \quad u + ( v + w ) = (u + v) + w$
			\item Existance of zero element: $\forall u \in V, \quad \exists 0 \in V$ such that $u + 0 = u$
			\item Existance of inverse element: $\forall u \in V, \quad \exists (-u) \in V$ such that $u + (-u) = 0$
			\item Commutative: $\forall u,v \in V, \quad u + v = v + u$
		\end{itemize}
		And the axioms for multiplication are
		\begin{itemize}
			\item Associative: $\forall a,b \in \mathbb{F}_4, v \in V, \quad a(bv) = (ab)v$.
			\item Distributive: $\forall a,b \in \mathbb{F}_4, v,u \in V$ then
					\[
						a(u+v) = au + av,
					\]
					\[
						(a+b)v = av + bv
					\]
			\item Existance of identity element: $1v = v \forall v \in V$
		\end{itemize}
	\end{defn}

@@

	\begin{thm}
		A nonempty subset $U$ of a vector space $V$ is a subspace if and only if $U$ is closed with respect to addition and scalar multiplication.
	\end{thm}

@@

	\subsection{Linear combinations}
	\begin{defn}
		A linear combination of the vectors from $X$ is an expression of the form $w = \sum_{i \in I} a_i u_i$ where $a_i \in \mathbb{F}$ (scalars) and $u_i \in X$ (vectors).
		If the set $X$ is infinite, them only finitely many $a_i$ are allowed to be nonzero. $w$ will of course be a vector, referred to as a linear combination of the $u_i$'s.
	\end{defn}

@@

\section{Bases and dimension}
	\begin{defn}
	\end{defn}

>>>>

	\subsection{Working with finite fields}
	In $\mathbb{F}_p = \mathbb{Z}_p$ you can simply do the operations in modulo $p$.
	\[
		x \oplus y := x + y mod p,
	\]
	\[
		x \otimes y := xy mod p
	\]
	Subtraction and division are substituted with addition and multiplication:
	\[
		x - y := x + (-y),
	\]
	\[
		\frac{x}{y} := xy^{-1}
	\]

	\subsubsection{Operations for $\mathbb{F}_4$}
	For any finite field you can use precomputed addition/multiplication tables.
	\[
		\begin{array}{c | c c c c}
			+ & 0 & 1 & a & b \\
			\hline
			0 & 0 & 1 & a & b \\
			1 & 1 & 0 & b & a \\ 
			a & a & b & 0 & 1 \\
			b & b & a & 1 & 0
		\end{array}
		\quad
		\begin{array}{c|cccc}
			\cdot & 0 & 1 & a & b \\
			\hline
			0 & 0 & 0 & 0 & 0 \\
			1 & 0 & 1 & a & b \\
			a & 0 & a & b & 1 \\
			b & 0 & b & 1 & a
		\end{array}
	\]
	In $\mathbb{F}_4$, note that $-0 = 0$, $-1 = 1$, $-a = a$, and $-b = b$.

\section{Vector Spaces}
	\begin{defn}
		A vector space over the field of scalars $\mathbb{F}_4$ is a set $V$, whose elements are 
		vectors, together with two binary operations addition and multiplication. The following axioms hold for addition
		\begin{itemize}
			\item Associative: $\forall u,v,w \in V, \quad u + ( v + w ) = (u + v) + w$
			\item Existence of zero element: $\forall u \in V, \quad \exists 0 \in V$ such that $u + 0 = u$
			\item Existence of inverse element: $\forall u \in V, \quad \exists (-u) \in V$ such that $u + (-u) = 0$
			\item Commutative: $\forall u,v \in V, \quad u + v = v + u$
		\end{itemize}
		And the axioms for multiplication are
		\begin{itemize}
			\item Associative: $\forall a,b \in \mathbb{F}_4, v \in V, \quad a(bv) = (ab)v$.
			\item Distributive: $\forall a,b \in \mathbb{F}_4, v,u \in V$ then
					\[
						a(u+v) = au + av,
					\]
					\[
						(a+b)v = av + bv
					\]
			\item Existence of identity element: $1v = v \forall v \in V$
		\end{itemize}
	\end{defn}

@@

	\begin{thm}
		A non-empty subset $U$ of a vector space $V$ is a subspace if and only if $U$ is closed with respect to addition and scalar multiplication.
	\end{thm}

@@

	\subsection{Linear combinations}
	\begin{defn}
		A linear combination of the vectors from $X$ is an expression of the form $w = \sum_{i \in I} a_i u_i$ 
		where $a_i \in \mathbb{F}$ (scalars) and $u_i \in X$ (vectors).	If the set $X$ is infinite, them only 
		finitely many $a_i$ are allowed to be non-zero. $w$ will of course be a vector, referred to as a linear 
		combination of the $u_i$'s.
	\end{defn}

@@

\section{Bases and dimension}
	\subsection{Linear independence}
	\begin{defn}
		If a non-zero linear combinatino of the vector from $X$ adds up to the zero vector then we say that $X$ is a linearly dependent set of vectors.
	\end{defn}
	Similarly,
	\begin{defn}
		The set $X$ is linearly independent if no nonzero linear combination of the vectors from $X$ sums to the zero vector.
	\end{defn}

	\subsection{Bases}
	\begin{defn}
		A basis of $V$ is a linearly indepedent spanning set for $V$.
	\end{defn}

	\subsection{Minimal spanning sets}
	\begin{thm}
		Suppose $X$ and $Y$ are subsets of a vector space $V$ and that $Y \subseteq X$. Then $<X> \subseteq <Y>$.
	\end{thm}

	\begin{thm}
		A set of vectors $X$ is a minimal spanning set for $U = <X>$ if and only if $X$ is linearly independent.
	\end{thm}

	\subsection{Bases always exist}
	\begin{thm}
		If $V$ is a vector space then $V$ contains at least one basis.
	\end{thm}

	\subsection{Size of a linearly independent set}
	\begin{thm}
		If a vector space $V$ has a finite basis of size $n$ then every linearly independent set of vectors in $V$ has a size at most $n$.
	\end{thm}

	\subsection{Dimension}
	\begin{crl}
		If $V$ has a finite spanning set then every basis in $V$ has the same finite size.
	\end{crl}

	\begin{defn}
		The dimension of a vector space $V$ is the size of an arbitrary basis in it.
	\end{defn}
	Note, we say $V$ is finite/infinitely dimensional depending on whether the size of the basis is finite/infinite.

	\begin{thm}
		A given set of $n$ vectors $v_1, v_2, ..., v_n$ from $\mathbb{F}^n$ is a basis if and only if the square matrix ($n \times n$) with rows $v_i$ has a non-zero determinant.
	\end{thm}

	\subsection{Coordinates}
